Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-09 report/report.tex
Add note on the origin of SLU

For the purpose of this project, the OSM road dataset has been sampled around Stockholm metropolitan area.
To assess and correct path widths and path node locations, the OSM building footprint dataset areound the same area has also been used.
As a reference dataset, the SLU map from the Swedish National Land Survey was used in comparison with the OSM map.
%TODO: What does SLU stand for?
The SLU map conatins only building and property footprints.
The exact map segments that were extracted were in both cases rectangular boundaries with the following coordinates in WGS84: (N: 59.42, E: 18.15, S: 59.23, W: 17.79).
Both datasets were collcted on March 18th, 2020.

>>>>

For the purpose of this project, the OSM road dataset has been sampled around Stockholm metropolitan area.
To assess and correct path widths and path node locations, the OSM building footprint dataset areound the same area has also been used.
As a reference dataset, the property map from the Swedish National Land Survey was used in comparison with the OSM map.
The reference map is provided by the Swedish University of Agricultural Sciences (SLU), and will be referred to in this report as the SLU map or the SLU dataset.
The SLU map conatins only building and property footprints.
The exact map segments that were extracted were in both cases rectangular boundaries with the following coordinates in WGS84: (N: 59.42, E: 18.15, S: 59.23, W: 17.79).
Both datasets were collcted on March 18th, 2020.
